\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-09-03 doc/sw-system.tex
Drafted performance section of discussion #44

In general, there are three places we can act to improve system performance:
educating the volunteers, assigning subjects for classification, and
interpreting the classification data. The plots in this section suggest that
...

@@

>>>>

In general, there are three places we can act to improve system performance:
educating the volunteers, assigning subjects for classification, and
interpreting the classification data. The plots in this section suggest that
...
\todo{Phil}{complete this thought, and update the text below, in the light of
the FP and the FN figures}

@@

Finally, there could be some performance gains to be made by improving the
SWAP agent model, or its implementation. In a future paper we plan to
investigate the use of the test images as well as the training images in
learning the agent confusion matrix elements (Davis et al, in preparation).
One might also consider looking at introducing more conditional dependences in
these elements, to allow for some classifiers having greater skill in one type
of lens than another, or, more generally, as a function of lens property (such
as color, brightness, and image separation). In the current model, all agents
are considered to be completely independent, whereas in fact we might expect
there to be significant clustering of the confusion matrix elements. A
hierarchical model for the crowd, with hyper-parameters describing the
distribution of confusion matrix elements across the population, may well
accelerate the agent learning process by including the notion of one agent
being likely to be similar to its neighbours. Finally, it is worth noting that
the model of \citet{IBCC} explicitly avoids the assumption of the agent
confusion matrix elements being constant in time, allowing the development of
volunteer skill to be more accurately tracked -- and that they did see some
time-evolution in the supernova zoo classifiers' skill. Finding a way to
incorporate such a learning model into SWAP, while retaining its statistically
online character is an interesting challenge for future work.
